How do school travel planning stakeholders frame active school travel in Ontario, Canada?

### 2021-06-24 AST-Framing-Ontario/AST-Framing-Ontario.Rmd
Moved analysis code to Results section

journal: "Journal of Transport & Health"
date: "`r Sys.Date()`"
bibliography: mybibfile.bib
#linenumbers: true
#numbersections: true
csl: elsevier-harvard.csl
output: rticles::elsevier_article
---

```{r, include=FALSE}
library(tm)
library(readr)
library(tools)
library(DiagrammeR)
library(kableExtra)
```

@@

2. Methods
===============

## 2.1. Case study: Ontario, Canada

## 2.2. Data retrieval

### 2.2.1. Policy documents

@@

```{r search-results, echo=FALSE}
data_tbl <- data.frame(
  Stakeholder = c("English school boards", "Municipal or regional governments", "Transportation Consortia"),
  Total = c("62", "62", "39"),
  Included = c("31", "25", "8")
)

kable(data_tbl,
      "latex",
      booktabs = TRUE,
      caption = "\\label{tab:search-results}Search results from the main stakeholder groups.") %>%
  kable_paper(full_width = F) %>%
  column_spec(1, bold = T, border_right = T) %>%
  column_spec(2, width = "30em") %>%
  column_spec(3, border_left = T) %>%
  kable_styling(latex_options = c("striped", "scale_down"))
```

Loading in clean corpus. These are the products of 'Data Pre-Processing.Rmd'
```{r}
load(file= "Corpus .rda/academic_corpus.rda")
load(file= "Corpus .rda/municipal_corpus.rda")
load(file= "Corpus .rda/consortium_corpus.rda")
load(file= "Corpus .rda/school_corpus.rda")
load(file= "Corpus .rda/policy_corpus.rda")
```

Municipal Bi/Trigrams
```{r}
# Converting corpus to tidytext data type 
td_municipal_corpus <- tidy(municipal_corpus)

@@

municipal_trigrams <- td_municipal_corpus %>%
  unnest_tokens(trigram, text, token = "ngrams", n = 3)
# Bigrams & Trigrams that are most common

top_municipal_bigrams <- municipal_bigrams %>%
  count(bigram, sort = TRUE)

@@

Consortium Bi/Trigrams
```{r}
# Converting corpus to tidytext data type 
td_consortium_corpus <- tidy(consortium_corpus)

@@

consortium_trigrams <- td_consortium_corpus %>%
  unnest_tokens(trigram, text, token = "ngrams", n = 3)
# Bigrams & Trigrams that are most common

top_consortium_bigrams <- consortium_bigrams %>%
  count(bigram, sort = TRUE)

@@

School board Bi/Trigrams
```{r}
# Converting corpus to tidytext data type 
td_school_corpus <- tidy(school_corpus)

@@

school_trigrams <- td_school_corpus %>%
  unnest_tokens(trigram, text, token = "ngrams", n = 3)
# Bigrams & Trigrams that are most common

top_school_bigrams <- school_bigrams %>%
  count(bigram, sort = TRUE)

@@

Policy Bi/Trigrams
```{r}
# Converting corpus to tidytext data type 
td_policy_corpus <- tidy(policy_corpus)

@@

policy_trigrams <- td_policy_corpus %>%
  unnest_tokens(trigram, text, token = "ngrams", n = 3)
# Bigrams & Trigrams that are most common

top_policy_bigrams <- policy_bigrams %>%
  count(bigram, sort = TRUE)

@@

Academic Bi/Trigrams
```{r}
# Converting corpus to tidytext data type 
td_academic_corpus <- tidy(academic_corpus)

@@

academic_trigrams <- td_academic_corpus %>%
  unnest_tokens(trigram, text, token = "ngrams", n = 3)
# Bigrams & Trigrams that are most common

top_academic_bigrams <- academic_bigrams %>%
  count(bigram, sort = TRUE)

@@

Municipal Bi-gram visualizations 
```{r}
municipal_bigrams_separated <- municipal_bigrams %>%
  separate(bigram, c("word1", "word2"), sep = " ")

@@

# Adjust the parameter below to filter out based on number of occurence
# Error will occur if n is outide the range of occurences

@@

Consortium Bi-gram visualizations 
```{r}
consortium_bigrams_separated <- consortium_bigrams %>%
  separate(bigram, c("word1", "word2"), sep = " ")

@@

School Board Bi-gram visualizations 
```{r}
school_bigrams_separated <- school_bigrams %>%
  separate(bigram, c("word1", "word2"), sep = " ")

@@

Policy Bi-gram visualizations 
```{r}
policy_bigrams_separated <- policy_bigrams %>%
  separate(bigram, c("word1", "word2"), sep = " ")

@@

Academic Bi-gram visualizations 
```{r}
academic_bigrams_separated <- academic_bigrams %>%
  separate(bigram, c("word1", "word2"), sep = " ")

@@

# Adjust the parameter below to filter out based on number of occurence
# Error will occur if n is outide the range of occurences

@@

At this point, the documents were imported into the corpus in `R` and added to a data frame for analysis. In the final step before analysis, we removed all blank spaces, punctuation, capitalization, and numbers. English stop words, as identified in a predetermined list by Lewis et al. [@R-tm], were removed.

## 2.3. Topic modelling

## 2.4. Summative content Analysis

## 2.5. Reproducibility

3. Results
===============

## 3.1. Word Frequency

## 3.2. Bigrams and Correlations

## 3.3. Policy content

4. Discussion
===============

## 4.1. Framing of AST in policy documents

## 4.2. Framing of AST in academic papers

## 4.3. Implications for School Travel Planning

@@

## 4.4. Limitations

5. Conclusion
===============

## 5.1. Future research

>>>>

journal: "Journal of Transport & Health"
date: "`r Sys.Date()`"
bibliography: mybibfile.bib
linenumbers: false
#numbersections: true
csl: elsevier-harvard.csl
output: rticles::elsevier_article
---

```{r load-packages, include=FALSE}
library(DiagrammeR)
library(dplyr)
library(ggraph)
library(ggplot2)
library(igraph)
library(kableExtra)
library(pdftools)
library(readr)
library(reshape2)
library(stringr)
library(text2vec)
library(textdata)
library(tidyr)
library(tidytext)
library(tm) 
library(tools)
library(topicmodels)
library(widyr)
library(word2vec)
library(wordcloud)
```

```{r load-data, include=FALSE}
load(file= "Corpus .rda/academic_corpus.rda")
load(file= "Corpus .rda/municipal_corpus.rda")
load(file= "Corpus .rda/consortium_corpus.rda")
load(file= "Corpus .rda/school_corpus.rda")
load(file= "Corpus .rda/policy_corpus.rda")
```

```{r package-bib, include=FALSE}
# This function is used to write a bibliography for the `R` packages used in the paper
knitr::write_bib(file = 'packages.bib')
```

  ***Background***:  
  ***Methods***:  
  ***Results***: 
  ***Conclusions***:

\newpage

@@

2. Data
===============

## 2.1. Data retrieval

### 2.1.1. Policy documents

@@

```{r policy-documents, echo=FALSE}
data_tbl <- data.frame(
  Stakeholder = c("English school boards", "Municipalities or regions", "Transportation consortia"),
  Total = c("62", "62", "39"),
  Included = c("31", "25", "8")
)

kable(data_tbl,
      "latex",
      booktabs = TRUE,
      caption = "\\label{tab:search-results}Search results from the main STP stakeholder groups.") %>%
  kable_paper(full_width = F) %>%
  column_spec(1, bold = T, border_right = T) %>%
  column_spec(2, width = "30em") %>%
  column_spec(3, border_left = T) %>%
  kable_styling(latex_options = c("striped", "scale_down"))
```

At this point, the documents were imported into the corpus in `R` and added to a data frame for analysis. In the final step before analysis, we removed all blank spaces, punctuation, capitalization, and numbers. English stop words, which are common words such as _and_ or _the_ as identified in a predetermined list by Lewis et al. [@R-tm] and other frequent terms in the documents like places were removed from the corpus.

3. Methods
===============

## 3.1. Case study: Ontario, Canada

## 3.2. Topic modelling

## 3.3. Summative content analysis

## 3.4. Reproducibility

4. Results
===============

```{r city-bigrams, echo=FALSE}
# Converting corpus to tidytext data type 
td_municipal_corpus <- tidy(municipal_corpus)

@@

municipal_trigrams <- td_municipal_corpus %>%
  unnest_tokens(trigram, text, token = "ngrams", n = 3)

# Bigrams and trigrams that are most common 
top_municipal_bigrams <- municipal_bigrams %>%
  count(bigram, sort = TRUE)

@@

```{r consortia-bigrams, echo=FALSE}

# Converting corpus to tidytext data type 
td_consortium_corpus <- tidy(consortium_corpus)

@@

consortium_trigrams <- td_consortium_corpus %>%
  unnest_tokens(trigram, text, token = "ngrams", n = 3)

# Bigrams and trigrams that are most common 
top_consortium_bigrams <- consortium_bigrams %>%
  count(bigram, sort = TRUE)

@@

```{r school-bigrams, echo=FALSE}

# Converting corpus to tidytext data type 
td_school_corpus <- tidy(school_corpus)

@@

school_trigrams <- td_school_corpus %>%
  unnest_tokens(trigram, text, token = "ngrams", n = 3)

# Bigrams and trigrams that are most common 
top_school_bigrams <- school_bigrams %>%
  count(bigram, sort = TRUE)

@@

```{r policy-bigrams, echo=FALSE}

# Converting corpus to tidytext data type 
td_policy_corpus <- tidy(policy_corpus)

@@

policy_trigrams <- td_policy_corpus %>%
  unnest_tokens(trigram, text, token = "ngrams", n = 3)

# Bigrams and trigrams that are most common 
top_policy_bigrams <- policy_bigrams %>%
  count(bigram, sort = TRUE)

@@

```{r academic-bigrams, echo=FALSE}

# Converting corpus to tidytext data type 
td_academic_corpus <- tidy(academic_corpus)

@@

academic_trigrams <- td_academic_corpus %>%
  unnest_tokens(trigram, text, token = "ngrams", n = 3)

# Bigrams and trigrams that are most common 
top_academic_bigrams <- academic_bigrams %>%
  count(bigram, sort = TRUE)

@@

```{r city-visual, echo=FALSE}
municipal_bigrams_separated <- municipal_bigrams %>%
  separate(bigram, c("word1", "word2"), sep = " ")

@@

# Adjust the parameter below to filter out based on number of occurrence

# Error will occur if n is outide the range of occurrences

@@

```{r consortia-visual, echo=FALSE}
consortium_bigrams_separated <- consortium_bigrams %>%
  separate(bigram, c("word1", "word2"), sep = " ")

@@

```{r school-visual, echo=FALSE}
school_bigrams_separated <- school_bigrams %>%
  separate(bigram, c("word1", "word2"), sep = " ")

@@

```{r policy-visual, echo=FALSE}
policy_bigrams_separated <- policy_bigrams %>%
  separate(bigram, c("word1", "word2"), sep = " ")

@@

```{r academic-visual, echo=FALSE}
academic_bigrams_separated <- academic_bigrams %>%
  separate(bigram, c("word1", "word2"), sep = " ")

@@

# Adjust the parameter below to filter out based on number of occurrence

# Error will occur if n is outside the range of occurrences

@@

```{r academic-term-frequency, echo=FALSE}
# Create new data frame with the cleaned corpus 
AcademicTextDF <- data.frame(text = sapply(academic_corpus, as.character), stringsAsFactors = FALSE)

it_train = itoken(AcademicTextDF$text, progressbar = FALSE)
academic_vocab = create_vocabulary(it_train)

# Cut out terms that have a minimum count of 5 
academic_vocab <- prune_vocabulary(academic_vocab, term_count_min = 5)
academic_vocab
```

## 4.1. Word Frequency

## 4.2. Bigrams and Correlations

## 4.3. Policy content

5. Discussion
===============

## 5.1. Framing of AST in policy documents

## 5.2. Framing of AST in academic papers

## 5.3. Implications for School Travel Planning

@@

## 5.4. Limitations

6.1. Conclusion
===============

## 6.1. Future research
